---
title: "iteration_and_listcols"
author: "ruby"
date: "2025-10-28"
output: github_document
---


```{r message = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Make a list 

```{r}
l = 
  list(
    vec_numeric = 1:23,
    char_vec = c("Ruby"),
    mat = matrix(1:8, nrow = 2, ncol = 4),
    summary = summary(rnorm(1000, mean = 4))
  )

l

l[[1]]

```

## Make a different list 

```{r}
list_normals = 
  list(
    a = rnorm(30, mean = 3, sd = 1),
    b = rnorm(30, mean = 30, sd = 1),
    c = rnorm(30, mean = 3, sd = 10),
    d = rnorm(30, mean = 3, sd = 4)
  )

list_normals
```

(copy and paste function from last time)

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("The input x should be numeric")
  }
  
  if(length(x) < 5) {
    stop("Only comupute mean and sd when the input has 5 or more numbers")
  }
  
  mean_x = mean(x, na.rm = TRUE)
  sd_x = sd(x, na.rm = TRUE)
  
  tibble(
    mean = mean_x, 
    sd = sd_x)
  
}
```

```{r}
mean_and_sd(list_normals[[1]])
```

Use a loop to iterate!

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_normals[[i]])
}

output
```


Use `map` to do the same thing. 

```{r}
output = map(list_normals, mean_and_sd)


output = map(list_normals, median)
```

Check out some `map` variants 

collapse maps into a dataframe 
```{r}
map_dfr(list_normals, mean_and_sd)
```

can keep track of an input id
```{r}
map_dfr(list_normals, mean_and_sd, .id = "sample")
```

make result of single numbers into a dataframe of single numbers 
```{r}
map_dbl(list_normals, median)
```

## LIST COLUMNS 

try to put my list into a dataframe 

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    sample = list_normals
  )
```

did this really work - can check using`pull()` 

```{r}
pull(listcol_df, sample)
```

apply `mean_and_sd`
```{r}
mean_and_sd(pull(listcol_df, sample)[[1]])
```

iterate using `map`
```{r}
map(pull(listcol_df, sample), mean_and_sd)
```

